\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Test Plan}
\author{Adeela}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section{Introduction}
%\subsection{}
This test plan has been created to check if our system conforms to all functional requirements and also to specify the types of testing which will be used to validate the functional requirements. This will also explain actions required on failed test cases and time line to perform testing of the system.
\section{Objectives and Tasks}
\subsection{Objectives}
The objective of testing our system is to provide adequate testing of functional requirements and to provide validation and behaviour of system under simulated condition. Exhaustive testing of system is not possible but we will use a diverse range of tests to find bugs and errors in the system including unit, functional, error and system testing. System is implemented using java which is platform independent language therefore cross platform testing will be performed too. Some automation testing will be used with manual testing to find bugs are errors in the system.
\subsection{Tasks}
\begin{itemize}
\item Identifying functional requirements and writing the tests cases.
\item Executing tests.
\item Record the failed test cases and reporting them to team.
\item Performing the re-test on failed test cases one bugs are fixed.
\end{itemize}
\section{Scope}
In context to our system, which is implemented using agent-based model it will be tested at three different levels of functionality.
\begin{itemize}
\item Actual agent behaviour: \hfill \\
Can be checked by changing environment variables around agents.
This forms functional requirements of the system as well. We have two agents in our system. \begin{enumerate}
\item Vehicles\hfill \\
Following function requirements will be tested in Vehicle class

\begin{itemize}
	\item Accelerate
	\item Move towards
	\item Get vehicle ahead
	\item Find best route
	\item Slow down
\end{itemize}

\item Traffic Lights
 \end{enumerate}
\item Runtime errors: \hfill \\
Elements and data loads at run time will form part of runtime testing. Giving all valid and invalid inputs and check results can check this. Following elements and data will be tested
\item Overall behaviour of system: \hfill \\
Checks that all agents of the system produce expected results in a given scenario. This will include testing of agent?s interaction with other components of environment (roads, traffic lights) when programme will be executed at run time.
\end{itemize}
\end{document}  